---
title: "Bechdel"
author: "Mine Çetinkaya-Rundel   \nModified by Tyler George"
output: github_document
---

In this mini analysis we work with the data used in the FiveThirtyEight story titled ["The Dollar-And-Cents Case Against Hollywood's Exclusion of Women"](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/).
Your task is to fill in the blanks denoted by `___`.

## Data and packages

We start with loading the packages we'll use.

```{r load-packages, message=FALSE}
library(fivethirtyeight)
library(tidyverse)
```

The dataset contains information on `r nrow(bechdel)` movies released between `r min(bechdel$year)` and `r max(bechdel$year)`.
However we'll focus our analysis on movies released between 1990 and 2013.

```{r}
bechdel90_13 <- bechdel %>% 
  filter(between(year, 1990, 2013))
```

There are `___` such movies.

The financial variables we'll focus on are the following:

-   `budget_2013`: Budget in 2013 inflation adjusted dollars
-   `domgross_2013`: Domestic gross (US) in 2013 inflation adjusted dollars
-   `intgross_2013`: Total International (i.e., worldwide) gross in 2013 inflation adjusted dollars

And we'll also use the `binary` and `clean_test` variables for **grouping**.

## Analysis

Let's take a look at how median budget and gross vary by whether the movie passed the Bechdel test, which is stored in the `binary` variable.

```{r message = FALSE}
bechdel90_13 %>%
  group_by(binary) %>%
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

Next, let's take a look at how median budget and gross vary by a more detailed indicator of the Bechdel test result.
This information is stored in the `clean_test` variable, which takes on the following values:

-   `ok` = passes test
-   `dubious`
-   `men` = women only talk about men
-   `notalk` = women don't talk to each other
-   `nowomen` = fewer than two women

```{r message = FALSE}
bechdel90_13 %>%
  #group_by(___) %>%
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

In order to evaluate how return on investment varies among movies that pass and fail the Bechdel test, we'll first create a new variable called `roi` as the ratio of the gross to budget.

```{r}
bechdel90_13 <- bechdel90_13 %>%
  mutate(roi = (intgross_2013 + domgross_2013) / budget_2013)
```

Let's see which movies have the highest return on investment.

```{r}
bechdel90_13 %>%
  arrange(desc(roi)) %>% 
  select(title, roi, year)
```

Below is a visualization of the return on investment by test result, however it's difficult to see the distributions due to a few extreme observations.

```{r warning = FALSE}
ggplot(data = bechdel90_13, 
       mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       x = "Detailed Bechdel result",
       y = "___",
       color = "Binary Bechdel result")
```

What are those movies with *very* high returns on investment?

```{r}
bechdel90_13 %>%
  filter(roi > 400) %>%
  select(title, budget_2013, domgross_2013, year)
```

Zooming in on the movies with `roi < ___` provides a better view of how the medians across the categories compare:

```{r warning = FALSE}
ggplot(data = bechdel90_13, mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       subtitle = "___", # Something about zooming in to a certain level
       x = "Detailed Bechdel result",
       y = "Return on investment",
       color = "Binary Bechdel result") +
  coord_cartesian(ylim = c(0, 15))
```

# Any Conclusions? 
We often have goals in mind when exploring data - it may be just to explore the data! Answer the following questions:

1) What is the "dubious" group? 

2) Compare the groups. How does the return on investment compare between those passing the test and those not? Give a full sentence answer. 

3) What problem is this anayliss trying to reveal? Is this plot, on its own, biased? 

3) What would you like to see in the data next? Give a full sentence answer. 

4) What ideas your group have for making this visualization even better? Think about color or formatting changes. 

4) What are the implications of this research in the real world? What is the intention of those that complied and retrived the data? Is their goal ethical? 

5) Was the data collected in a legal way that protected indivduals rights as humans? Does this article give enough information to asses this? 

6) Are there any variables that may not be ethical to use? Are we prepared to answer such questions? 
