---
title: "Text analysis <br> `r emo::ji('page_with_curl')`"
author: ""
output:
  xaringan::moon_reader:
    css: "../slides.css"
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      highlightStyle: solarized-light
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

```{r child = "../setup.Rmd"}
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

class: middle

# Tidytext analysis

---

## Packages

In addition to `tidyverse` we will be using four other packages today

```{r message=FALSE}
library(tidytext)
library(genius)
library(wordcloud)
library(DT)
```

---

## Tidytext

- Using tidy data principles can make many text mining tasks easier, more effective, and consistent with tools already in wide use.
- Learn more at https://www.tidytextmining.com/.

---

## What is tidy text?

There Is a Light That Never Goes Out
The Smiths 

```{r}
text <- c("Take me out tonight",
          "Where there's music and there's people",
          "And they're young and alive",
          "Driving in your car",
          "I never never want to go home",
          "Because I haven't got one",
          "Anymore")

text
```

---

## What is tidy text?

```{r}
text_df <- tibble(line = 1:7, text = text)

text_df
```

---

## What is tidy text?

```{r}
text_df %>%
  unnest_tokens(word, text)
```

---

class: middle

# What are you listening to?

---

## From class survey(s)

> "What is your favorite song? (exclusing those with derogatory words)"

.midi[
```{r message=FALSE}
listening <- read_csv("data/listening.csv")
listening
```
]

---

## Looking for commonalities

.midi[
```{r}
listening %>%
  unnest_tokens(word, songs) %>%
  count(word, sort = TRUE)
```
]

---

## Stop words

- In computing, stop words are words which are filtered out before or after processing of natural language data (text).
- They usually refer to the most common words in a language, but there is not a single list of stop words used by all natural language processing tools.

---

## English stop words

```{r}
get_stopwords()
```

---

## Spanish stop words

```{r}
get_stopwords(language = "es")
```

---

## Various lexicons

See `?get_stopwords` for more info.

.midi[
```{r}
get_stopwords(source = "smart")
```
]

---

## Back to: Looking for commonalities

.small[
```{r}
listening %>%
  unnest_tokens(word, songs) %>%
  anti_join(stop_words) %>%                           #<<
  filter(!(word %in% c("1", "2", "3", "4", "5"))) %>% #<<
  count(word, sort = TRUE)
```
]

---

## Top 20 common words in songs

.pull-left[
.small[
```{r message=FALSE}
top20_songs <- listening %>%
  unnest_tokens(word, songs) %>%
  anti_join(stop_words) %>%
  filter(
    !(word %in% c("1", "2", "3", "4", "5"))
    ) %>%
  count(word) %>%
  top_n(20)
```
]
]
.pull-right[
.midi[
```{r}
top20_songs %>%
  arrange(desc(n))
```
]
]
---

## Visualizing commonalities: bar chart

.midi[
```{r echo=FALSE}
top20_songs %>%
  ggplot(aes(x = fct_reorder(word, n), y = n)) +
  geom_col() +
  labs(x = "Common words", y = "Count") +
  coord_flip()
```
]

---

... the code

```{r eval=FALSE}
ggplot(top20_songs, aes(x = fct_reorder(word, n), y = n)) +
  geom_col() +
  labs(x = "Common words", y = "Count") +
  coord_flip()
```


---

## Visualizing commonalities: wordcloud

```{r echo=FALSE, out.width="80%"}
set.seed(1234)
wordcloud(words = top20_songs$word, 
          freq = top20_songs$n, 
          colors = brewer.pal(5,"Blues"),
          random.order = FALSE, 
          rot.per = 0.35,
          scale = c(2, 0.5))
```

---

... and the code

```{r eval=FALSE}
set.seed(1234)
wordcloud(words = top20_songs$word, 
          freq = top20_songs$n, 
          colors = brewer.pal(5,"Blues"),
          random.order = FALSE)
```

---

## Ok, so what does our people like? 

Let look at our word cloud or bar chart to see.

```{r,eval = F}
top_artist <- "sheeran"

str_subset(listening$songs, top_artist)

```

---

class: middle

# Analyzing lyrics of one artist
## Let's get more data

We'll use the **genius** package to get song lyric data from [Genius](https://genius.com/).

- `genius_album()`: download lyrics for an entire album
- `add_genius()`: download lyrics for multiple albums

---

## Singers most recent-ish albums
We need to fill this in with our classes favorite artist. Lets look at their most recent alblum. 
```{r cache=TRUE, message=FALSE, warning=FALSE}
artist_albums <- tribble(
  ~artist,      ~album,
  "Ed Sheeran", "No.6 Collaborations Project")

artist <- artist_albums %>%
  add_genius(artist, album, "album")

# attach the lyrics (the genius function no longer supported)
artist_lyrics <- read_csv('data/artistlyrics.csv')
artist <- artist %>%
  mutate(track_title = str_squish(track_title))%>%
  left_join(artist_lyrics,by="track_title")

glimpse(artist)

```

---

## Songs in the four albums

.small[
```{r echo=FALSE}
options(htmltools.preserve.raw = FALSE)
artist %>%
  distinct(album, track_title) %>%
  datatable(options = list(dom = "p"))
```
]

---

## Tidy up your lyrics!

```{r}
artist_lyrics <- artist %>%
  unnest_tokens(word, lyric)

artist_lyrics
```

---

## What are the most common words?

```{r}
artist_lyrics %>%
  count(word, sort = TRUE)
```

---

## Remove Stop Words

.midi[
```{r}
artist_lyrics %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```
]

---

```{r echo=FALSE, message=FALSE, out.width="80%"}
artist_lyrics %>%
  anti_join(stop_words) %>%
  count(word)%>%
  top_n(20) %>%
  ggplot(aes(fct_reorder(word, n), n)) +
    geom_col() +
    labs(title = "Frequency of Artists lyrics",
         y = "",
         x = "") +
    coord_flip()
```

---

... and the code

```{r eval=FALSE}
artist_lyrics %>%
  anti_join(stop_words) %>%
  count(word)%>%
  top_n(20) %>%
  ggplot(aes(fct_reorder(word, n), n)) +
    geom_col() +
    labs(title = "Frequency of Ed Artists lyrics",
         y = "",
         x = "") +
    coord_flip()
```

---

class: middle

# Sentiment analysis

---

## Sentiment analysis

- One way to analyze the sentiment of a text is to consider the text as a combination of its individual words 
- and the sentiment content of the whole text as the sum of the sentiment content of the individual words

---

## Sentiment lexicons

.pull-left[
```{r}
get_sentiments("afinn")
```
]
.pull-right[
```{r}
get_sentiments("bing") 
```
]

---

## Sentiment lexicons

.pull-left[
```{r}
get_sentiments("nrc")
```
]
.pull-right[
```{r}
get_sentiments("loughran") 
```
]

---

class: middle

## Categorizing sentiments

---

## Sentiments in Artists lyrics

.midi[
```{r}
artist_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, word, sort = TRUE)
```
]

---

class: middle

**Goal:** Find the top 10 most common words with positive and negative sentiments.

---

### Step 1: Top 10 words for each sentiment

.midi[
```{r message=FALSE}
artist_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, word) %>%
  group_by(sentiment) %>%
  top_n(10) 
```
]

---

### Step 2: `ungroup()`

.midi[
```{r message=FALSE}
artist_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, word) %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup()
```
]

---

### Step 3: Save the result

```{r message=FALSE}
artist_top10 <- artist_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, word) %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup()
```

---

class: middle

**Goal:** Visualize the top 10 most common words with positive and negative sentiments.

---

### Step 1: Create a bar chart

.midi[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = word, y = n, fill = sentiment)) +
  geom_col()
```
]

---

### Step 2: Order bars by frequency

.midi[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col()
```
]

---

### Step 3: Facet by sentiment

.midi[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col() +
  facet_wrap(~ sentiment)
```
]

---

### Step 4: Free the scales!

.midi[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col() +
  facet_wrap(~ sentiment, scales = "free")
```
]

---

### Step 4: Flip the coordinates

.midi[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col() +
  facet_wrap(~ sentiment, scales = "free") +
  coord_flip()
```
]

---

### Step 5: Clean up labels

.small[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col() +
  facet_wrap(~ sentiment, scales = "free") +
  coord_flip() +
  labs(title = "Sentiments in Ed Sheeran's lyrics", x = "", y = "")
```
]

---

### Step 6: Remove redundant info

.small[
```{r message=FALSE, out.width="80%"}
artist_top10 %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = sentiment)) +
  geom_col() +
  facet_wrap(~ sentiment, scales = "free") +
  coord_flip() +
  labs(title = "Sentiments in Ed Sheeran's lyrics", x = "", y = "") +
  guides(fill = "none") 
```
]

---

class: middle

## Scoring sentiments

---

## Assign a sentiment score

.small[
```{r}
artist_lyrics %>%
  anti_join(stop_words) %>%
  left_join(get_sentiments("afinn")) 
```
]

---

```{r message=FALSE}
artist_lyrics %>%
  anti_join(stop_words) %>%
  left_join(get_sentiments("afinn")) %>%
  filter(!is.na(value)) %>%
  group_by(album) %>%
  summarise(total_sentiment = sum(value)) %>%
  arrange(total_sentiment)
```

---

```{r echo=FALSE, message=FALSE, warning=FALSE}
artist_lyrics %>%
  anti_join(stop_words) %>%
  left_join(get_sentiments("afinn")) %>%
  filter(!is.na(value)) %>%
  group_by(album, track_title) %>%
  summarise(total_sentiment = sum(value)) %>%
  ungroup() %>%
  arrange(total_sentiment) %>%
  mutate(
    track_title = str_remove(track_title, "by (.*)") %>% str_trim(),
    track_title = str_remove(track_title, "\\(.*\\)") %>% str_trim(),
    total_sentiment_sign = if_else(total_sentiment < 0, "negative", "positive")
  ) %>%
  ggplot(aes(x = reorder(track_title, total_sentiment), y = total_sentiment, fill = total_sentiment_sign)) +
  geom_col() +
  facet_wrap(~album, ncol = 2, scales = "free") +
  guides(fill = "none") +
  coord_flip() +
  labs(x = "", y = "", 
    title = "Total sentiment score of Ed Sheeran's tracks",
    subtitle = "Scored with AFINN sentiment lexicon")
```

---

## Acknowledgements

- Julia Silge: https://github.com/juliasilge/tidytext-tutorial
- Julia Silge and David Robinson: https://www.tidytextmining.com/
- Josiah Parry: https://github.com/JosiahParry/genius
