---
title: "Exam 1 DSC 223 Fall 2021 Block 1"
author: "[ENTER NAME HERE]"
date: "Due: 12/3/2021 at 11:59 PM"
output: 
  github_document: 
    fig_height: 4
    fig_width: 7
---

```{r setup, include = FALSE}
# set the echo option to FALSE to see how the document looks with the code suppressed
knitr::opts_chunk$set(echo = TRUE)
```

## Academic Honesty Statement

I, ____________, hereby state that I have not communicated with or gained information in any way from my classmates or anyone other than the Professor or TA during this exam, and that all work is my own.

## Load data
Complete the function to read the data in from the data folder.

```{r data-load}
youtube <- read.csv('___')
```


### Answer the following about the day, month, and year you were born in (number format). Change the **eval=F** to T. Do not change the **include**.
```{r sample-data,include = F, eval=F}
d <-__
m <-__
y <- ____

set.seed(d+m+y)

# The data you should be using for the exam:
youtube1 <- tuesdata$youtube[sample.int(247,247,T),]
```

You should use this new YouTube data for the remainder of the exam. 

## Load packages

```{r load-packages, message=FALSE}
# load required packages here
```

## Questions 

### Question 1

[Enter code and narrative here.]

### Question 2

[Enter code and narrative here.]

### Question 3

[Enter code and narrative here.]

### Question 4

[Enter code and narrative here.]

### Question 5

[Enter code and narrative here.]

### Question 6

[Enter code and narrative here.]

### Question 7

[Enter code and narrative here.]

### Question 8

[Enter code and narrative here.]

### Question 9

[Enter code and narrative here.]

### Bonus

[Enter code and narrative here.]


